---
title: "<center>Behavioral Data Science<br>Project - Part I</center>"
author: "<center>Avisek Choudhury<br>Ben Corriveau<br>Cindy Nikolai</center>"
date: "<center>10/12/2020</center>"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Research Question 1
Customers were asked to rate their opinion of the "SFO Airport as a whole" on a scale from 1 ("unacceptable") to 5 ("outstanding"). The executives want to know if there are patterns across the satisfied or dissatisfied customers based on demographic characteristics, such as sex, age group, and income level.

```{r readData, message=FALSE, warning=FALSE, error=TRUE}
#Import the libraries
library(tidyverse)
library(haven)
library(plotly)
library(reshape2)
library(lmtest)
library(lme4)
library(psych)
library(GPArotation)
library(ggcorrplot)
```

```{r}
#Read the data set
sfoDf <- read_delim('/Users/benjamincorriveau/OneDrive/School/BehavioralDS/SFO_survey_withText.txt', delim="\t")
```

Now convert the columns for age, income and sex.
```{r , message=FALSE, warning=FALSE, error=TRUE}
#Convert the Sex
sfoDf['Gender'] <- ifelse(sfoDf$Q18 == 1, "Male",
                          ifelse(sfoDf$Q18 == 2, "Female", "Blank"))
#Convert the Age Group column
sfoDf['Age_Group'] <- ifelse(sfoDf$Q17 == 1, "Under 18", 
       ifelse(sfoDf$Q17 == 2, "18-24", 
              ifelse(sfoDf$Q17 == 3, "25-34", 
                     ifelse(sfoDf$Q17 == 4, "35-44", 
                            ifelse(sfoDf$Q17 == 5, "45-54", 
                                   ifelse(sfoDf$Q17 == 6, "55-64", 
                                          ifelse(sfoDf$Q17 == 7, "65 and Over",
                                                ifelse(sfoDf$Q17 == 8, "Don't Know/Refused", 
                                                       ifelse(sfoDf$Q17 == 0, "Blank", "NA")))))))))

#Convert the Income Column
sfoDf['Income'] <- ifelse(sfoDf$Q19 == 1, "Under $50,000", 
                          ifelse(sfoDf$Q19 == 2, "$50,000-$100,00",
                                 ifelse(sfoDf$Q19 == 3, "$100,001-$150,000",
                                        ifelse(sfoDf$Q19 == 4, "Over $150,000",
                                               ifelse(sfoDf$Q19 == 5, "Other", "Blank")))))
```


Let's take a look at satisfaction ratings (Question 6n) grouped by various attributes (gender, income, age, etc.)
```{r}
satisfaction_data <- sfoDf %>%
  select('Gender','Age_Group','Income','Q6N') %>% 
  melt(., id.vars=c('Age_Group','Gender','Income'), value.name = 'Score') %>% 
  select(-'variable') %>% 
  na.omit(.)

satisfaction_data$Income <- factor(satisfaction_data$Income,levels = c('Under $50,000',"$50,000-$100,00","$100,001-$150,000","Over $150,000","Other","Blank"))

satisfaction_data$Age_Group <- factor(satisfaction_data$Age_Group, levels = c( "Under 18","18-24","25-34","35-44","45-54","55-64","65 and Over","Don't Know/Refused","Blank", "NA"))
```

We will start by looking at responses grouped by Gender and Income
```{r}
ggplot(satisfaction_data, aes(x=as.factor(Score), fill=Income)) + 
  geom_bar(stat='count') +
  facet_wrap(~Gender) + 
  labs(title="Satisfaction Score by Gender/Income", x='Score', y='Count')
```

We can see that the most common response for "How does SFO Airport rate as a whole" was a 4, which is one step below the highest score .  Worth noting here is that while 6 is an option, it represents "Have never used or visited/not applicable" so we consider a 5 the highest score.  The largest number of respondents who gave SFO a 4 appear to have income within $50,000 - $100,00. This could be because they liked it best, or because they are the largest respondent group.  We also see that male respondents had a higher proportion of '3' responses than '4', the opposite being true for females.  We will want to test this theory later in a regression model

Now let's take a look at the responses grouped by Income and Age
```{r}
ggplot(satisfaction_data, aes(x=as.factor(Score), fill=Age_Group)) + 
  geom_bar(stat='count') +
  facet_wrap(~Income) +
  labs(title="Satisfaction Score by Income/Age", x='Score', y='Count')
```
We see a similar pattern in this data, with 4 being the most common response for all income levels.  

Though we have a general idea of the distribution, we want to run a regression model to see if we see any kind of pattern.
```{r}
lm_score <- lm(Score ~ Gender + Age_Group + Income,data = satisfaction_data)
summary(lm_score)
```

Based on this simple regression, we see that only 4 of the demographic categories have a statistically significant impact on the overall rating: `GenderMale`, `Income$50,000-$100,00`, `Income$100,001-$150,000`, and `IncomeOver $150,000`.  Each of these 4 categories appears to have an overall negative influence on the satisfaction score.


# Research Question 2
The executives also want to know if customer satisfaction can be broken down into different attributes of the airport. Knowing this will help the team target specific strengths or areas of improvement. The central feature the customer satisfaction survey is a 14-question portion of the survey asking customers to rate satisfaction with different aspects of the airport (see Question 6 in the data directory). The executives want you to perform a quantitative analysis to determine if there are broad themes that emerge from this part of the survey.

To answer this question, we will conduct a factor analysis to see if patterns emerge.  We will need to look at the responses to all parts of Question 6:

How does SFO rate on each of the following attributes? 
  6a. Artwork and exhibitions
  6b. Restaurants
  6c. Retail shops and concessions
  6d. Signs and directions inside SFO
  6e. Escalators/elevators/moving walkways
  6f. Information on screens/monitors
  6g. Information booths (lower level near baggage claim) 
  6h. Information booths (upper level – departure area) 
  6i. Signs and directions on SFO airport roadways
  6j. Airport parking facilities
  6k. AirTrain
  6l. Long term parking lot shuttle
  6m. Airport rental car center
  6n. SFO Airport as a whole

```{r}
short_survey <- sfoDf %>% 
  select(Q6A:Q6N)
```

Let's take a look at a correlation plot to see if any patterns jump out.
```{r}
short_survey %>% 
  cor(., use="complete.obs") %>% 
  ggcorrplot(type = "lower")
```
Immediately we see that questions about the information booths (6H and 6G) are almost perfectly positively correlated, likely meaning the information booth quality is the same, regardless of its location.  We also see there is a string positive correlation among many of the travel and parking related responses (6J, 6K, 6L, 6M).

What we see in the correlation plot leads us to think there may be some themes here, so we will do a more thorough factor analysis to see if this holds true.  To begin, we will see how many factors will be best to use.
```{r}
short_survey %>% 
  nfactors()
```
From the data above, we see that either 3 or 5 factors will likely be best.  We will try both to see if there is a meaningful difference.
```{r}
surveyFA_3 <- short_survey %>% 
  fa(., nfactors = 3, rotate = "promax")

surveyFA_3$loadings
```

With 3 factors, we see that people who answered positively about shopping, navigational aides, and moving walkways (6A,6B,6C,6D,6E,6F) also tended to answer positively for the overall score (6N).  One interpretation of factor MR1 as people are often in a hurry to catch their flight and appreciate being able to move through the airport quickly.  Another option is that people are appreciative of the food and shopping.

We also see in factor MR2 the same parking and transportation correlation we saw in the plot.  People who answered positively about the parking also did so about airport transportation services (6I,6J,6K,6L,6M).  However, positive responses in these questions did not appear to effect the overall score.

Finally, we see that factor MR3 is the grouping of information booths we saw in the correlation plot.  Positive responses about either floor's information booth tended match positive responses for the other.  However, positive responses in these questions did not appear to effect the overall score.

Next we will review 5 factors to see if any further patterns emerge.
```{r}
surveyFA_5 <- short_survey %>% 
  fa(., nfactors = 5, rotate = "promax")

surveyFA_5$loadings
```

We see mostly the same results here, but now the shopping, food, and navigational information responses are in different factors, with navigation and moving walkways (MR1) having a larger positive correlation with a positive overall score.  Food and shopping (MR4) also seems to be related to a positive overall score, but to a lesser extent.

We also see now that we have separate factors for airport travel (6I,6K,6L,6M), in factor MR5, and parking accommodations (6I,6J,6L), in factor MR2.  Even though they are separate, there is a bit of overlap in 6L and 6I.

With 5 factors, it becomes a bit more clear what most respondents seem to favor: clear navigational aides and moving walkways (MR1).  While shopping is also important, the priority for travelers seems to be ease/speed of navigating within the airport. 


