---
title: "<center>Behavioral Data Science<br>Project - Group 6</center>"
author: "<center>Avisek Choudhury<br>Ben Corriveau<br>Cindy Nikolai</center>"
date: "<center>11/06/2020</center>"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
Airport executives and state and local officials are curious about customer satisfaction at San Francisco International Airport. Business and tourist travelers are a huge source of revenue for the city. SFO is in a prime location relative to other west-coast cities, and it is well situated as a long-term layout spot for international travel to Asia. Because of this, identifying current strengths of the airport and areas for improvement are critical to increasing traffic and revenue.

Marketing executives developed a survey and administered it to customers over the previous year. SFO invested a lot of time and resources in collected comprehensive data for 3,234 customers on 100 variables. They have now hired us as their data science consultants to gain insights into these data. The SFO team is not well-versed in data science methodology, but they have a few key areas of interest for us to look into. 

## Part A
### Hypothesis/Hypotheses
### Question 1
Customers were asked to rate their opinion of the "SFO Airport as a whole" on a scale from 1 ("unacceptable") to 5 ("outstanding"). The executives want to know if there are patterns across the satisfied or dissatisfied customers based on demographic characteristics, such as sex, age group, and income level.  We are theorizing that there will be distinct patterns that emerge in the deomgraphic data, but are yet unsure of what they will show.

### Question 2
The executives also want to know if customer satisfaction can be broken down into different attributes of the airport. Knowing this will help the team target specific strengths or areas of improvement. The central feature the customer satisfaction survey is a 14-question portion of the survey asking customers to rate satisfaction with different aspects of the airport (see Question 6 in the data directory). The executives want us to perform a quantitative analysis to determine if there are broad themes that emerge from this part of the survey.


#### Data Description/EDA
Start with a general overview of the data (sample size, important variables, etc); describe what you can about the variables needed to address the executives’ questions; provide a small number of tables or figures with EDA output relevant to your research. Mention any insights gleaned from EDA that altered your original hypothesis or changed your analysis approach.

#### Analysis plan
Detail the specific analyses that will address these research questions. (1-2 paragraphs, or numbered/bulleted list)

#### Results
Run models - but do not necessarily post all code chunks and all outputs. Organize and summarize the most crucial results. Describe the analytic results (regression coefficients, p-values, comparison of test error rates, interpretation of clusters, benefit of multiple imputation, interpretation of sentiment and topics, etc) of the various analyses you ran. Interpret the meaning of the result. (length open)

#### Discussion
Relate the results directly to the prompts posed by the SFO executives. Did you address the research questions? Did the results match your expectations, or did you find something different from you were expecting? What are the strengths of your chosen analysis, and what are the potential limitations of the method used or issues in the data?

# Part B
##Research Question and Hypothesis
Briefly describe your own general research question and specific hypothesis behind it.

#### EDA
Describe any key variabls for your research question that were not used in Part A, and/or summarize EDA findings from Part A.

#### Analysis Plan
Describe the method chosen to address your own research question and why.

#### Results
Same as descibed in Part A - summarize important results and how the chosen method is evaluated, and interpret findings.

#### Discussion
Relate results back to your broader research question.

# Appendix

#### Load Data and Libraries
```{r readData, message=FALSE, warning=FALSE, error=TRUE}
#Import the libraries
library(tidyverse)
library(haven)
library(plotly)
library(reshape2)
library(lmtest)
library(lme4)
library(psych)
library(GPArotation)
library(ggcorrplot)
library(tidytext)
library(wordcloud2)
library(sentimentr) 
library(lexicon)
library(magrittr)
library(tidyr)

#Read the data set
sfoDf <- read_delim('/Users/benjamincorriveau/OneDrive/School/BehavioralDS/SFO_survey_withText.txt', delim="\t")
```

#### EDA 
Let's count the missing rows for each column to get an idea of missingness.
```{r countingNA, message=FALSE, warning=FALSE, error=TRUE }
sapply(sfoDf, function(x) sum(is.na(x)))
```

We see lot of columns with huge no of missing values. Let's check the columns with more than 50% values are missing.
```{r countingNA50, message=FALSE, warning=FALSE, error=TRUE }
#Count the NA or missing Rows for each columns
unlist(sapply(sfoDf, function(x) { 
  if (sum(is.na(x)) > length(x)* 0.5)  
    return (sum(is.na(x))) 
  }))
```

So we see there are 40 columns out of 101 columns has more than 50% missing values.

#### Research Question 1

The first step is to convert the columns for age, income and sex into something easier to read.
```{r , message=FALSE, warning=FALSE, error=TRUE}
#Convert the Sex
sfoDf['Gender'] <- ifelse(sfoDf$Q18 == 1, "Male",
                          ifelse(sfoDf$Q18 == 2, "Female", "Blank"))
#Convert the Age Group column
sfoDf['Age_Group'] <- ifelse(sfoDf$Q17 == 1, "Under 18", 
       ifelse(sfoDf$Q17 == 2, "18-24", 
              ifelse(sfoDf$Q17 == 3, "25-34", 
                     ifelse(sfoDf$Q17 == 4, "35-44", 
                            ifelse(sfoDf$Q17 == 5, "45-54", 
                                   ifelse(sfoDf$Q17 == 6, "55-64", 
                                          ifelse(sfoDf$Q17 == 7, "65 and Over",
                                                ifelse(sfoDf$Q17 == 8, "Don't Know/Refused", 
                                                       ifelse(sfoDf$Q17 == 0, "Blank", "NA")))))))))

#Convert the Income Column
sfoDf['Income'] <- ifelse(sfoDf$Q19 == 1, "Under $50,000", 
                          ifelse(sfoDf$Q19 == 2, "$50,000-$100,00",
                                 ifelse(sfoDf$Q19 == 3, "$100,001-$150,000",
                                        ifelse(sfoDf$Q19 == 4, "Over $150,000",
                                               ifelse(sfoDf$Q19 == 5, "Other", "Blank")))))
```


Let's take a look at satisfaction ratings (Question 6n) grouped by various attributes (gender, income, age, etc.)
```{r}
satisfaction_data <- sfoDf %>%
  select('Gender','Age_Group','Income','Q6N') %>% 
  melt(., id.vars=c('Age_Group','Gender','Income'), value.name = 'Score') %>% 
  select(-'variable') %>% 
  na.omit(.)

satisfaction_data$Income <- factor(satisfaction_data$Income,levels = c('Under $50,000',"$50,000-$100,00","$100,001-$150,000","Over $150,000","Other","Blank"))

satisfaction_data$Age_Group <- factor(satisfaction_data$Age_Group, levels = c( "Under 18","18-24","25-34","35-44","45-54","55-64","65 and Over","Don't Know/Refused","Blank", "NA"))
```

We will start by looking at responses grouped by Gender and Income
```{r}
ggplot(satisfaction_data, aes(x=as.factor(Score), fill=Income)) + 
  geom_bar(stat='count') +
  facet_wrap(~Gender) + 
  labs(title="Satisfaction Score by Gender/Income", x='Score', y='Count')
```

We can see that the most common response for "How does SFO Airport rate as a whole" was a 4, which is one step below the highest score.  Worth noting here is that while 6 is an option, it represents "Have never used or visited/not applicable" so we consider a 5 the highest score.  The largest number of respondents who gave SFO a 4 appear to have income within `$50,000 - $100,000`. This could be because they liked it best, or because they are the largest respondent group.  We also see that male respondents had a higher proportion of '3' responses than '5', the opposite being true for females.  We will want to test this theory later in a regression model.

Now let's take a look at the responses grouped by Income and Age
```{r}
ggplot(satisfaction_data, aes(x=as.factor(Score), fill=Age_Group)) + 
  geom_bar(stat='count') +
  facet_wrap(~Income) +
  labs(title="Satisfaction Score by Income/Age", x='Score', y='Count')
```
We see a similar pattern in this data, with 4 being the most common response for all income levels.  

Though we have a general idea of the distribution, we want to run a regression model to see if we see any kind of pattern.
```{r}
lm_score <- lm(Score ~ Gender + Age_Group + Income,data = satisfaction_data)
summary(lm_score)
```

Based on this simple regression, we see that only 4 of the demographic categories have a statistically significant impact on the overall rating: `GenderMale`, `Income$50,000-$100,00`, `Income$100,001-$150,000`, and `IncomeOver $150,000`.  Each of these 4 categories appears to have an overall negative influence on the satisfaction score.


#### Research Question 2

To answer this question, we will conduct a factor analysis to see if patterns emerge.  We will need to look at the responses to all parts of Question 6:

How does SFO rate on each of the following attributes? 
  6a. Artwork and exhibitions
  6b. Restaurants
  6c. Retail shops and concessions
  6d. Signs and directions inside SFO
  6e. Escalators/elevators/moving walkways
  6f. Information on screens/monitors
  6g. Information booths (lower level near baggage claim) 
  6h. Information booths (upper level – departure area) 
  6i. Signs and directions on SFO airport roadways
  6j. Airport parking facilities
  6k. AirTrain
  6l. Long term parking lot shuttle
  6m. Airport rental car center
  6n. SFO Airport as a whole

```{r}
short_survey <- sfoDf %>% 
  select(Q6A:Q6N)
```

Let's take a look at a correlation plot to see if any patterns jump out.
```{r}
short_survey %>% 
  cor(., use="complete.obs") %>% 
  ggcorrplot(type = "lower")
```
Immediately we see that questions about the information booths (6H and 6G) are almost perfectly positively correlated, likely meaning the information booth quality is the same, regardless of its location.  We also see there is a string positive correlation among many of the travel and parking related responses (6J, 6K, 6L, 6M).

What we see in the correlation plot leads us to think there may be some themes here, so we will do a more thorough factor analysis to see if this holds true.  To begin, we will see how many factors will be best to use.
```{r}
short_survey %>% 
  nfactors()
```
From the data above, we see that either 3 or 4 factors will likely be best.  We will try both to see if there is a meaningful difference.
```{r}
surveyFA_3 <- short_survey %>% 
  fa(., nfactors = 3, rotate = "promax")

surveyFA_3$loadings
```

With 3 factors, we see that people who answered positively about shopping, navigational aides, and moving walkways (6A,6B,6C,6D,6E,6F) also tended to answer positively for the overall score (6N).  One interpretation of factor MR1 as people are often in a hurry to catch their flight and appreciate being able to move through the airport quickly.  Another option is that people are appreciative of the food and shopping.

We also see in factor MR2 the same parking and transportation correlation we saw in the plot.  People who answered positively about the parking also did so about airport transportation services (6I,6J,6K,6L,6M).  However, positive responses in these questions did not appear to effect the overall score.

Finally, we see that factor MR3 is the grouping of information booths we saw in the correlation plot.  Positive responses about either floor's information booth tended match positive responses for the other.  However, positive responses in these questions did not appear to effect the overall score.

Next we will review 4 factors to see if any further patterns emerge.
```{r}
surveyFA_4 <- short_survey %>% 
  fa(., nfactors = 4, rotate = "promax")

surveyFA_4$loadings
```

We see mostly the same results here, but now the shopping, food, and navigational information responses are in different factors, with navigation and moving walkways (MR1) having a larger positive correlation with a positive overall score.  Food and shopping (MR4) also seems to be related to a positive overall score, but to a lesser extent.

We see the same results for both factors MR2 (transportation and parking) and MR3 (information booths).

With 4 factors, it becomes a bit more clear what most respondents seem to favor: clear navigational aides and moving walkways (MR1).  While shopping is also important, the priority for travelers seems to be ease/speed of navigating within the airport. 

#### Research Question #3

Free-response comments, either good or bad, were collected in addition to the 14-item quantitative survey. The executives are not quite sure how to examine it without going through individual surveys one by one, but they want you to see if there are any concepts or insights that arise from these responses. Do the free responses relate to the findings in a) or b) at all?


For sentiment analysis let's have a look at the combined comment column in the given dataset.

```{r , message=FALSE, warning=FALSE, error=TRUE}
#Comment Column
sfoDf$Q7_text_All %>% 
  na.omit %>% 
  head(10)
```

Let's remove the forward slash and hyphens from the comments and replace that with blank space.

```{r, message=FALSE, warning=FALSE, error=TRUE}
#Remove the Slash
sfoDf$Q7_text_All <- gsub(pattern = "/", 
                          replacement = " ", 
                          sfoDf$Q7_text_All)
#Remove the hyphens
sfoDf$Q7_text_All <- gsub(pattern = "-", 
                          replacement = " ", 
                          sfoDf$Q7_text_All)
#Verify the data
sfoDf$Q7_text_All %>% 
  na.omit %>% 
  head(10)
```

Let's check the count of distinct words used by each age group. We can remove the stop words before do the count.

```{r, message=FALSE, warning=FALSE}
#Word Count by each Inmate
wordDf <- sfoDf %>% 
  select(Q7_text_All, Q17, Age_Group) %>% 
   rename(Age = Q17,
         Comments = Q7_text_All) %>% 
  unnest_tokens(word, Comments) %>% 
  anti_join(stop_words) %>% 
  na.omit() %>% 
  group_by(Age_Group, Age, word) %>% 
  summarise(count = n())
#Check the data set
head(wordDf, n = 20)
```

Let's count positive and negative words for each age group and calculate the sentiment.

```{r , message=FALSE, warning=FALSE}
#Count positive and negative words
wordSent_bing <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Age_Group, Age, sentiment) %>% 
  count(sentiment)  %>% 
  spread(sentiment, n, fill = 0) %>% 
  mutate(sentiment = positive - negative)
#Print the dataset
head(wordSent_bing, n= 10)
```

Let's plot the positive and negative sentient count for each age group .

```{r , message=FALSE, warning=FALSE}
#Generate the Dataset for the Plot
plotDf <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Age_Group, Age, sentiment) %>% 
  count(sentiment) %>% 
  rename(count = n)
#Generate the Barplot for the Positive/Negative Sentiment
#For Each Age Group
ggplot(plotDf, aes(Age_Group), ylim(-30:30)) + 
geom_bar(data = subset(plotDf, sentiment == "positive"), 
   aes(y = count, fill = sentiment), stat = "identity", position = "dodge") +
geom_bar(data = subset(plotDf, sentiment == "negative"), 
   aes(y = -count, fill = sentiment), stat = "identity", position = "dodge") + 
geom_hline(yintercept = 0,colour = "grey90") + 
  #Now Add the Tect to it
geom_text(data = subset(plotDf, sentiment == "positive"), 
      aes(Age_Group, count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = 1.5, size=4) +
geom_text(data = subset(plotDf, sentiment == "negative"), 
      aes(Age_Group, -count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = -.5, size=4) +
    coord_cartesian(ylim = c(-30, 30))

```
We can see across all age range the negative sentiment is slightly higher than the positive sentiment.

Now instead of ` bing` we can use ` affin` which assigns a value positive/negative to each word and calculate the average sentiment for age group we have.

```{r, message=FALSE, warning=FALSE}
#Calculate Average sentiment for each inmate
avgSentAgeGrp <- wordDf %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(Age_Group) %>% 
  summarise( totalWords = sum(count), sentSum = sum(value)) %>% 
  mutate(Avg_Sentiment = sentSum / totalWords)
#Print the dataset
head(avgSentAgeGrp, n=20)
```

Here also we see the average sentiment is negative almost all age range except the population under 18.

Now let's analyze the sentiments by gender.

```{r, message=FALSE, warning=FALSE, error=TRUE}
#Word Count by each Inmate
wordDf <- sfoDf %>% 
  select(Gender,  Q7_text_All) %>% 
   rename(Comments = Q7_text_All) %>% 
  unnest_tokens(word, Comments) %>% 
  anti_join(stop_words) %>% 
  na.omit() %>% 
  group_by(Gender, word) %>% 
  summarise(count = n())
#Check the data set
head(wordDf, n = 20)
```

Let's count positive and negative words for each sex and calculate the sentiment.

```{r , message=FALSE, warning=FALSE}
#Count positive and negative words
wordSent_bing <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Gender, sentiment) %>% 
  count(sentiment)  %>% 
  spread(sentiment, n, fill = 0) %>% 
  mutate(sentiment = positive - negative)
#Print the dataset
head(wordSent_bing, n= 10)
```

The sentiment is negative for both males and females. Let's plot the data we generated above.

```{r , message=FALSE, warning=FALSE}
#Generate the Dataset for the Plot
plotDf <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Gender, sentiment) %>% 
  count(sentiment) %>% 
  rename(count = n)
#Generate the Barplot for the Positive/Negative Sentiment
#For Each Age Group
ggplot(plotDf, aes(Gender), ylim(-20:20)) + 
geom_bar(data = subset(plotDf, sentiment == "positive"), 
   aes(y = count, fill = sentiment), stat = "identity", position = "dodge") +
geom_bar(data = subset(plotDf, sentiment == "negative"), 
   aes(y = -count, fill = sentiment), stat = "identity", position = "dodge") + 
geom_hline(yintercept = 0,colour = "grey90") + 
  #Now Add the Tect to it
geom_text(data = subset(plotDf, sentiment == "positive"), 
      aes(Gender, count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = 1.5, size=4) +
geom_text(data = subset(plotDf, sentiment == "negative"), 
      aes(Gender, -count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = -.5, size=4) +
    coord_cartesian(ylim = c(-20, 20))
```

Let's use ` affin` again and calculate the average sentiment for each sex.

```{r, message=FALSE, warning=FALSE}
#Calculate Average sentiment for each inmate
avgSentSex <- wordDf %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(Gender) %>% 
  summarise( totalWords = sum(count), sentSum = sum(value)) %>% 
  mutate(Avg_Sentiment = sentSum / totalWords)
#Print the dataset
head(avgSentSex, n=20)
```



Let's check the count of distinct words used by each income group and remove the stop words before do the count.

```{r, message=FALSE, warning=FALSE}
#Word Count by each Inmate
wordDf <- sfoDf %>% 
  select(Q7_text_All, Income) %>% 
   rename(Comments = Q7_text_All) %>% 
  unnest_tokens(word, Comments) %>% 
  anti_join(stop_words) %>% 
  na.omit() %>% 
  group_by(Income, word) %>% 
  summarise(count = n())
#Check the data set
head(wordDf, n = 20)
```

Let's count positive and negative words for each income group and calculate the sentiment.

```{r , message=FALSE, warning=FALSE}
#Count positive and negative words
wordSent_bing <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Income, sentiment) %>% 
  count(sentiment)  %>% 
  spread(sentiment, n, fill = 0) %>% 
  mutate(sentiment = positive - negative)
#Print the dataset
head(wordSent_bing, n= 10)
```

The sentiment is dominantly negative for all income group.

We can plot this data as well.

```{r , message=FALSE, warning=FALSE}
#Generate the Dataset for the Plot
plotDf <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Income, sentiment) %>% 
  count(sentiment) %>% 
  rename(count = n)
#Generate the Barplot for the Positive/Negative Sentiment
#For Each Age Group
ggplot(plotDf, aes(Income), ylim(-20:20)) + 
geom_bar(data = subset(plotDf, sentiment == "positive"), 
   aes(y = count, fill = sentiment), stat = "identity", position = "dodge") +
geom_bar(data = subset(plotDf, sentiment == "negative"), 
   aes(y = -count, fill = sentiment), stat = "identity", position = "dodge") + 
geom_hline(yintercept = 0,colour = "grey90") + 
  #Now Add the Tect to it
geom_text(data = subset(plotDf, sentiment == "positive"), 
      aes(Income, count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = 1.5, size=4) +
geom_text(data = subset(plotDf, sentiment == "negative"), 
      aes(Income, -count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = -.5, size=4) +
    coord_cartesian(ylim = c(-20, 20))

```

We can use ` affin` again and calculate the average sentiment for all income groups.

```{r, message=FALSE, warning=FALSE}
#Calculate Average sentiment for each inmate
avgSentIncome <- wordDf %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(Income) %>% 
  summarise( totalWords = sum(count), sentSum = sum(value)) %>% 
  mutate(sentiment = sentSum / totalWords)
#Print the dataset
head(avgSentIncome, n=20)
```

#### Part B

