---
title: "<center>Behavioral Data Science<br>Project - Part II</center>"
author: "<center>Avisek Choudhury<br>Ben Corriveau<br>Cindy Nikolai</center>"
date: "<center>11/06/2020</center>"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part A - Question 3

Free-response comments, either good or bad, were collected in addition to the 14-item quantitative survey. The executives are not quite sure how to examine it without going through individual surveys one by one, but they want you to see if there are any concepts or insights that arise from these responses. Do the free responses relate to the findings in a) or b) at all?
 

```{r readData, message=FALSE, warning=FALSE, error=TRUE}
#Import the libraries
library(tidyverse)
library(haven)
library(plotly)
library(reshape2)
library(tidytext)
library(wordcloud2)
library(sentimentr) 
library(lexicon)
library(magrittr)
library(tidyr)

#Read the data set
sfoDf <- read_delim('C:/MSDS/Fall 2020/Behavioral Data Science/Project/SFO_survey_withText.txt', delim="\t")
head(sfoDf)
```


```{r countingNA, message=FALSE, warning=FALSE, error=TRUE }
#Count the NA or missing Rows for each columns
sapply(sfoDf, function(x) sum(is.na(x)))
```

We see lot of columns with huge no of missing values. Let's check the columns with more than 50% values are missing.

```{r countingNA50, message=FALSE, warning=FALSE, error=TRUE }
#Count the NA or missing Rows for each columns
unlist(sapply(sfoDf, function(x) { 
  if (sum(is.na(x)) > length(x)* 0.5)  
    return (sum(is.na(x))) 
  }))
```

So we see there are 40 columns out of 101 columns has more than 50% missing values.

Now convert the columns for age, income and sex.

```{r , message=FALSE, warning=FALSE, error=TRUE}
#Convert the Sex
sfoDf['Gender'] <- ifelse(sfoDf$Q18 == 1, "Male",
                          ifelse(sfoDf$Q18 == 2, "Female", "Blank"))
#Convert the Age Group column
sfoDf['Age_Group'] <- ifelse(sfoDf$Q17 == 1, "Under 18", 
       ifelse(sfoDf$Q17 == 2, "18-24", 
              ifelse(sfoDf$Q17 == 3, "25-34", 
                     ifelse(sfoDf$Q17 == 4, "35-44", 
                            ifelse(sfoDf$Q17 == 5, "45-54", 
                                   ifelse(sfoDf$Q17 == 6, "55-64", 
                                          ifelse(sfoDf$Q17 == 7, "65 and Over",
                                                ifelse(sfoDf$Q17 == 8, "Don't Know/Refused", 
                                                       ifelse(sfoDf$Q17 == 0, "Blank", "NA")))))))))

#Convert the Income Column
sfoDf['Income'] <- ifelse(sfoDf$Q19 == 1, "Under $50,000", 
                          ifelse(sfoDf$Q19 == 2, "$50,000-$100,00",
                                 ifelse(sfoDf$Q19 == 3, "$100,001-$150,000",
                                        ifelse(sfoDf$Q19 == 4, "Over $150,000",
                                               ifelse(sfoDf$Q19 == 5, "Other", "Blank")))))
```

For sentiment analysis let's have a look at the combined comment column in the given dataset.

```{r , message=FALSE, warning=FALSE, error=TRUE}
#Comment Column
sfoDf$Q7_text_All %>% 
  na.omit %>% 
  head(10)
```

Let's remove the forward slash and hyphens from the comments and replace that with blank space.

```{r, message=FALSE, warning=FALSE, error=TRUE}
#Remove the Slash
sfoDf$Q7_text_All <- gsub(pattern = "/", 
                          replacement = " ", 
                          sfoDf$Q7_text_All)
#Remove the hyphens
sfoDf$Q7_text_All <- gsub(pattern = "-", 
                          replacement = " ", 
                          sfoDf$Q7_text_All)
#Verify the data
sfoDf$Q7_text_All %>% 
  na.omit %>% 
  head(10)
```

Let's check the count of distinct words used by each age group. We can remove the stop words before do the count.

```{r, message=FALSE, warning=FALSE}
#Word Count by each Inmate
wordDf <- sfoDf %>% 
  select(Q7_text_All, Q17, Age_Group) %>% 
   rename(Age = Q17,
         Comments = Q7_text_All) %>% 
  unnest_tokens(word, Comments) %>% 
  anti_join(stop_words) %>% 
  na.omit() %>% 
  group_by(Age_Group, Age, word) %>% 
  summarise(count = n())
#Check the data set
head(wordDf, n = 20)
```

Let's count positive and negative words for each age group and calculate the sentiment.

```{r , message=FALSE, warning=FALSE}
#Count positive and negative words
wordSent_bing <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Age_Group, Age, sentiment) %>% 
  count(sentiment)  %>% 
  spread(sentiment, n, fill = 0) %>% 
  mutate(sentiment = positive - negative)
#Print the dataset
head(wordSent_bing, n= 10)
```

Let's plot the positive and negative sentient count for each age group .

```{r , message=FALSE, warning=FALSE}
#Generate the Dataset for the Plot
plotDf <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Age_Group, Age, sentiment) %>% 
  count(sentiment) %>% 
  rename(count = n)
#Generate the Barplot for the Positive/Negative Sentiment
#For Each Age Group
ggplot(plotDf, aes(Age_Group), ylim(-30:30)) + 
geom_bar(data = subset(plotDf, sentiment == "positive"), 
   aes(y = count, fill = sentiment), stat = "identity", position = "dodge") +
geom_bar(data = subset(plotDf, sentiment == "negative"), 
   aes(y = -count, fill = sentiment), stat = "identity", position = "dodge") + 
geom_hline(yintercept = 0,colour = "grey90") + 
  #Now Add the Tect to it
geom_text(data = subset(plotDf, sentiment == "positive"), 
      aes(Age_Group, count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = 1.5, size=4) +
geom_text(data = subset(plotDf, sentiment == "negative"), 
      aes(Age_Group, -count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = -.5, size=4) +
    coord_cartesian(ylim = c(-30, 30))

```
We can see across all age range the negative sentiment is slightly higher than the positive sentiment.

Now instead of ` bing` we can use ` affin` which assigns a value positive/negative to each word and calculate the average sentiment for age group we have.

```{r, message=FALSE, warning=FALSE}
#Calculate Average sentiment for each inmate
avgSentAgeGrp <- wordDf %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(Age_Group) %>% 
  summarise( totalWords = sum(count), sentSum = sum(value)) %>% 
  mutate(Avg_Sentiment = sentSum / totalWords)
#Print the dataset
head(avgSentAgeGrp, n=20)
```

Here also we see the average sentiment is negative almost all age range except the population under 18.

Now let's analyze the sentiments by gender.

```{r, message=FALSE, warning=FALSE, error=TRUE}
#Word Count by each Inmate
wordDf <- sfoDf %>% 
  select(Gender,  Q7_text_All) %>% 
   rename(Comments = Q7_text_All) %>% 
  unnest_tokens(word, Comments) %>% 
  anti_join(stop_words) %>% 
  na.omit() %>% 
  group_by(Gender, word) %>% 
  summarise(count = n())
#Check the data set
head(wordDf, n = 20)
```

Let's count positive and negative words for each sex and calculate the sentiment.

```{r , message=FALSE, warning=FALSE}
#Count positive and negative words
wordSent_bing <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Gender, sentiment) %>% 
  count(sentiment)  %>% 
  spread(sentiment, n, fill = 0) %>% 
  mutate(sentiment = positive - negative)
#Print the dataset
head(wordSent_bing, n= 10)
```

The sentiment is negative for both males and females. Let's plot the data we generated above.

```{r , message=FALSE, warning=FALSE}
#Generate the Dataset for the Plot
plotDf <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Gender, sentiment) %>% 
  count(sentiment) %>% 
  rename(count = n)
#Generate the Barplot for the Positive/Negative Sentiment
#For Each Age Group
ggplot(plotDf, aes(Gender), ylim(-20:20)) + 
geom_bar(data = subset(plotDf, sentiment == "positive"), 
   aes(y = count, fill = sentiment), stat = "identity", position = "dodge") +
geom_bar(data = subset(plotDf, sentiment == "negative"), 
   aes(y = -count, fill = sentiment), stat = "identity", position = "dodge") + 
geom_hline(yintercept = 0,colour = "grey90") + 
  #Now Add the Tect to it
geom_text(data = subset(plotDf, sentiment == "positive"), 
      aes(Gender, count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = 1.5, size=4) +
geom_text(data = subset(plotDf, sentiment == "negative"), 
      aes(Gender, -count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = -.5, size=4) +
    coord_cartesian(ylim = c(-20, 20))
```

Let's use ` affin` again and calculate the average sentiment for each sex.

```{r, message=FALSE, warning=FALSE}
#Calculate Average sentiment for each inmate
avgSentSex <- wordDf %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(Gender) %>% 
  summarise( totalWords = sum(count), sentSum = sum(value)) %>% 
  mutate(Avg_Sentiment = sentSum / totalWords)
#Print the dataset
head(avgSentSex, n=20)
```



Let's check the count of distinct words used by each income group and remove the stop words before do the count.

```{r, message=FALSE, warning=FALSE}
#Word Count by each Inmate
wordDf <- sfoDf %>% 
  select(Q7_text_All, Income) %>% 
   rename(Comments = Q7_text_All) %>% 
  unnest_tokens(word, Comments) %>% 
  anti_join(stop_words) %>% 
  na.omit() %>% 
  group_by(Income, word) %>% 
  summarise(count = n())
#Check the data set
head(wordDf, n = 20)
```

Let's count positive and negative words for each income group and calculate the sentiment.

```{r , message=FALSE, warning=FALSE}
#Count positive and negative words
wordSent_bing <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Income, sentiment) %>% 
  count(sentiment)  %>% 
  spread(sentiment, n, fill = 0) %>% 
  mutate(sentiment = positive - negative)
#Print the dataset
head(wordSent_bing, n= 10)
```

The sentiment is dominantly negative for all income group.

We can plot this data as well.

```{r , message=FALSE, warning=FALSE}
#Generate the Dataset for the Plot
plotDf <- wordDf %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(Income, sentiment) %>% 
  count(sentiment) %>% 
  rename(count = n)
#Generate the Barplot for the Positive/Negative Sentiment
#For Each Age Group
ggplot(plotDf, aes(Income), ylim(-20:20)) + 
geom_bar(data = subset(plotDf, sentiment == "positive"), 
   aes(y = count, fill = sentiment), stat = "identity", position = "dodge") +
geom_bar(data = subset(plotDf, sentiment == "negative"), 
   aes(y = -count, fill = sentiment), stat = "identity", position = "dodge") + 
geom_hline(yintercept = 0,colour = "grey90") + 
  #Now Add the Tect to it
geom_text(data = subset(plotDf, sentiment == "positive"), 
      aes(Income, count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = 1.5, size=4) +
geom_text(data = subset(plotDf, sentiment == "negative"), 
      aes(Income, -count, group=sentiment, label=count),
        position = position_dodge(width=0.9), vjust = -.5, size=4) +
    coord_cartesian(ylim = c(-20, 20))

```

We can use ` affin` again and calculate the average sentiment for all income groups.

```{r, message=FALSE, warning=FALSE}
#Calculate Average sentiment for each inmate
avgSentIncome <- wordDf %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(Income) %>% 
  summarise( totalWords = sum(count), sentSum = sum(value)) %>% 
  mutate(sentiment = sentSum / totalWords)
#Print the dataset
head(avgSentIncome, n=20)
```
